Single-step Hybrid Predition

### 2017-02-01 reports/transformed_kernel_predictions.Rmd
Add outlook on Bustos-Korts_2016

   -   Genomic data do not clearly perform better than pedigree data except for 
     ADF and FAT.

   -   Transcripts perform poorly for DMC and STA.

@@

   -   Predictive abilities for the combination of pedigree, SNP and 
     transcriptomic data "ped100-snp77-mrna42" seem to be the result of the
     predictive abilities of the individual predictors weighted by their share
     of the genotypes. 
     For example 
     $$r(\text{ped100-snp77-mrna42}) = r(\text{ped100}) * (1 - 0.77) +
     r(\text{snp77}) * (0.77 - 0.42) + r(\text{mrna42}) * 0.42$$

@@

   -   Predictive abilities for FAT and the predictor combination
     "ped100-snp77-mrna42" are difficult to explain.

>>>>

   -   Genomic data perform decisively better than pedigree data for DMY, ADF 
     and FAT.

   -   Relative to pedigree and genomic data, transcripts perform poorly for 
     DMC and STA.

@@

   -   Predictive abilities for the combination of pedigree, SNP and 
     transcriptomic data "ped100-snp77-mrna42" seem to be the sum of the
     predictive abilities of the individual predictors weighted by their share
     of the genotypes. 
     For example 
     $$r(\text{ped100-snp77-mrna42}) = r(\text{ped100}) * (1 - 0.77) +
     r(\text{snp77}) * (0.77 - 0.42) + r(\text{mrna42}) * 0.42$$

@@

   -   Predictive abilities for FAT and the predictor combination
     "ped100-snp77-mrna42" are difficult to explain. **Suggestions???**
